Removing nonlinear batch effects using adversarial deep neural networks

### 2019-02-13 thesis.tex
Add figures files

\documentclass[titlepage]{article}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{hyperref}
\usepackage[square,numbers]{natbib}
\bibliographystyle{unsrtnat}

@@

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/network}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}

@@

>>>>

\documentclass[notitlepage]{article}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{hyperref}
\usepackage[square,numbers]{natbib}
\usepackage[nomarkers]{endfloat}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,footskip=0.25in]{geometry}
\linespread{1.5}
\bibliographystyle{unsrtnat}
% TODO: increase spacing, decrease margins.

@@

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/adjuster_workflow}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/batch_accuracy}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/network}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mmd}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mnist}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mse}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/network}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/pca}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/training_loss}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/true_class_accuracy}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/network}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/tsne}
	\caption{Network architecture}
	\label{simulationfigure}
\end{figure}

@@

% TODO: put all the figures in here

\subsection{Effects are still detectable after ComBat and scale adjusting}

\subsection{Effects not removed by other adjusters are removed by Confounded}

\subsection{Important signal is not removed by Confounded}
